Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2018-06-09 paper/galsize_paper.tex
Revised text to address minor comment 1

We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM). See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter. To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}. For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.  Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$ dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}. As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").

>>>>

We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM). See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter. To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}. For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.  Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$ dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}.

We include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies"). Orphans play an important in our model due to the sensitivity of $\rhalf$-dependent clustering upon the satellite fraction. In our fiducial model whose results are shown in the main body of the text, half of the disrupted subhalos are selected prior to application of SHAM. We explore alternative treatments of orphans in the appendix.
